\mythesistitleNOTSYNPOSIS

### 2012-01-07 src/020chap2.tex
chapter 2 - started set system side of things. see diff for more details.

\begin{table}[htbp]
  \centering
   \includegraphics[scale=0.5]{../img/cophistory.png} % TEMPORARY

  \caption[\figtabsize A brief history of \COP research]{\figtabsize A
    brief history of \COP research \temptext{ OLD IMG - PLACEHOLDER - A LATEX
    TABLE WILL REPLACE THIS + WILL BE UPDATED }}
  \label{tab:cophistory}
\end{table}

@@

\begin{figure}[htbp]
  \centering
  \begin{tabular}[h]{lr}
    \begin{tabular}[h]
      {>{\columncolor{\tblhcolor}} l lllllllllll|}
      \hline
      $r_1$   &\un &0   &\un &0   &0   &0    &0   \\
      $r_2$   &\un &0   &\un &0   &0   &0    &0   \\
      $r_3$   &\un &0   &0   &\un &0   &0    &0   \\
      $r_4$   &\un &0   &0   &\un &0   &0    &0   \\
      $r_5$   &\un &0   &0   &0   &0   &0    &0   \\
      $r_6$   &\un &\un &0   &0   &0   &0    &0   \\
      $r_7$   &0   &\un &0   &0   &0   &\un  &0   \\
      $r_8$   &0   &\un &0   &0   &\un &\un  &0   \\
      $r_9$   &0   &\un &0   &0   &\un &\un  &0   \\
      $r_{10}$ &0   &\un &0   &0   &\un &\un  &\un \\
      $r_{11}$ &0   &\un &0   &0   &\un &0    &\un \\
      \hline
    \end{tabular}
    &
    \includegraphics[scale=0.3]{../img/pqtree.png}

  \end{tabular}

  \caption[\figtabsize An example for \PQtree]{\figtabsize An example for \PQtree.
    Permuting the order of the left child of the root, we see that
    \temptext{(d,a,b,c,e,f,g,h,i,j,k)} is a \COP order. Reversing the
    order of the right child of the root, we see that
    \temptext{(a,b,c,d,e,f,k,j,h,i,g) } is yet another \COP order. \temptext{PLACEHOLDER IMG.}
    \cite[Fig.~1\endnote{\cite{mcc04}illustrates \COP on rows. Our
      convention in this document is \COP on columns and thus example
      matrix has been transposed. }]{mcc04}}
  \label{fig:pqtree}
\end{figure}

@@

After the invention of \PQtrees, there has been several variants of
the same with either simpler procedure of construction, like \PCtree
\cite{wlh01}\endnote{First appeared in
  \cite{wlh92_isaac}.\tnote{check}} or a generalization of it, like
generalized \PQtree \cite{mcc04}. \PQRtree is another generalization
of \PQtree by \cite{mm96,mpt98}. There algorithm was improved by
\cite{tm05} \tnote{improved in terms of
  what?}. % describes an improved algorithm to
% build PQR trees.

\temptext{Expand a little more on PC trees and PQR trees.}

We will see more of \PQRtree in Section~\ref{sec:surveycertalgo}

\temptext{
  \begin{enumerate}[ -I-]
  \item  Variations - PQR, PC etc. [MM96, Hsu01, McC04]\\
    Generalized PQ trees McC04 - brief. Will be elaborated in
    Section~\ref{sec:surveycertalgo}\\
    Hsu also invented PC trees \cite{wlh01}\tnote{This result first
      appeared inproc ISAAC92} which is claimed to be much easier to
    implement.
  \item Set theoretic characterizations [Hsu02, NS09]\\
    \cite{wlh02} describes the simpler algorithm for
    COT.\tnote[pressing]{in terms of what?}\\
    \cite{nsnrs09} describes a characterization of consecutive-ones
    property solely based on the cardinality properties of the set
    representations of the columns (rows); every column (row) is
    equivalent to a set that has the row (column) indices of the rows
    (columns) that have one entries in this column (row). This is
    interesting and relevant, especially to this thesis because it
    simplifies COT to a great degree by reducing the solution search
    space owing to the a simple set theoretic characterization.\\
  \item Parallel algorithms [AS95, BS03, CY91]
  \end{enumerate}

@@

\section{Certifying Algorithms}
\label{sec:surveycertalgo}
%\tnote{Expand on sec:appcertalgo} \tnote{ (certification McC04
%theme)}

@@

>>>>

\def\tabparboxw{10cm}
\begin{table}[htbp]
  \centering
  {
    \fontencoding{OT1}\fontfamily     {cmss}\selectfont
    % \sffamily
    \footnotesize
    % \includegraphics[scale=0.5]{../img/cophistory.png} % TEMPORARY

   \begin{tabular}[h]{lll}
     \hline
     \hline
     % 
     1899 & \parbox[t]{\tabparboxw}{ First mention of \COP} & \cite{p59}  \\

     \rowcolor[gray]{0.8} %
     1951 & \parbox[t]{\tabparboxw}{ Heuristics for COT} & \cite{wsr51} \\

     1965 & \parbox[t]{\tabparboxw}{ First polynomial time algorithm
       for \COP testing} & \cite{fg65} \\

     \rowcolor[gray]{0.8} %
     1972 & \parbox[t]{\tabparboxw}{ Characterization for \COP -- forbidden
       submatrices} &
     \cite{at72} \\

     1976 & \parbox[t]{\tabparboxw}{ First linear time algorithm for COT --
       \PQtree} &
     \cite{bl76} \\

     \rowcolor[gray]{0.8} %
     1992 & \parbox[t]{\tabparboxw}{ Linear
       time algorithm COT without \PQtree} & \cite{wlh02}\endnote{First
       published in \cite{wlh02isaac92}} \\

     2001 & \parbox[t]{\tabparboxw}{\PCtree\ -- a simplification of
       \PQtree} & \cite{wlh01,hm03} \\

     \rowcolor[gray]{0.8} %     
     1996 & \parbox[t]{\tabparboxw}{\PQRtree\ -- generalization of
       \PQtree for any binary matrix regardless of its \COP status} &
     \cite{mm96} \\

     1998 & \parbox[t]{\tabparboxw}{ Almost linear time to construct
       \PQRtree} & \cite{mpt98} \\

     \rowcolor[gray]{0.8} %
     2004 & \parbox[t]{\tabparboxw}{ A certifying algorithm for no
       \COP.\\ Generalized \PQtree.} & \cite{mcc04} \\

     2009 & \parbox[t]{\tabparboxw}{ Set theoretic, cardinality based
       characterization of \COP\ -- ICPIA} & \cite{nsnrs09} \\

     \rowcolor[gray]{0.8} %
     2010 & \parbox[t]{\tabparboxw}{ Logspace \COP testing} &
     \cite{kklv10}\\ 
     \hline
     \hline
   \end{tabular}
 }
 \caption[\figtabsize A brief history of \COP research]{\figtabsize A
   brief history of \COP research }
 \label{tab:cophistory}
\end{table}

@@

\figpqtree

@@

After the invention of \PQtrees, there has been several variants of
the same with either simpler procedure of construction, like \PCtree
\cite{wlh01} or a generalization of it, like
generalized \PQtree \cite{mcc04}. \PQRtree is another generalization
of \PQtree by \cite{mm96,mpt98}. There algorithm was improved by
\cite{tm05} \tnote{improved in terms of
  what?}. % describes an improved algorithm to
% build PQR trees.

\temptext{Expand a little more on PC trees and PQR trees.?}

We will see more of generalized \PQtree in Section~\ref{sec:surveycertalgo}.

\temptext{
  \begin{enumerate}[ -I-]
   \item Parallel algorithms [AS95, BS03, CY91]
  \end{enumerate}
}

@@

%\section{Certifying Algorithms}
\section{COP for set systems}
\label{sec:surveycertalgo}
%\tnote{Expand on sec:appcertalgo} \tnote{ (certification McC04
%theme)}

Section~\ref{xxx} mentions how a binary matrix naturally maps to a
system of sets.  A set can be constructed for each column of matrix
with its elements being those row indices at which the column has \un
s. Thus the collection of sets corresponding each column of the matrix
forms a set system with universe as the set of all row indices of the
matrix.  This simple construction is formally described in
Definition~\ref{def:matrixsetsystem}.

\begin{definition}%
  \label{def:matrixsetsystem}%
  [\emph{Set system of a binary matrix}.] Let $M$ be a binary matrix
  of order $n \times m$ % , $r_i, i \in [n]$ be the rows in $M$
  and $\{c_i \mid i \in [m]\}$ be the columns in $M$. A set system
  $\cF_{M} = \{S_i \mid S_i \subseteq [n], i \in [m]\}$ is defined
  such that for every column $c_i$ of $M$, set $S_i = \{j \mid m_{ji}
  = \un \}$. The collection $\cF_M$ is the set system of matrix $M$.
\end{definition}

Thus the idea of \cop naturally maps to set sytems as well\endnote{As
  seen in Section~\ref{theCourseScheduleExample}} as
Definition~\ref{def:copforsets} states. This is equivalent to \COP for
matrices seen in Definition~\ref{def:copmatrix}.

\begin{definition}%
  \label{def:copforsets}%
  [\emph{\Cop for set systems% \cite{mcc04}
  }.] A set system $\cF$ with universe $U$ has the \cop if it is
  possible to assign a linear order to $U$ where each set $S \in \cF$
  is an interval in the linear order.\tnote[important]{NOT formal
    enough.}
\end{definition}

@@

Set theoretic characterizations [Hsu02, NS09]\\
    \cite{wlh02} describes the simpler algorithm for
    COT.\tnote[pressing]{in terms of what?}\\
    \cite{nsnrs09} describes a characterization of consecutive-ones
    property solely based on the cardinality properties of the set
    representations of the columns (rows); every column (row) is
    equivalent to a set that has the row (column) indices of the rows
    (columns) that have one entries in this column (row). This is
    interesting and relevant, especially to this thesis because it
    simplifies COT to a great degree by reducing the solution search
    space owing to the a simple set theoretic characterization.\\
